### 2023-01-17 output/DiD/tables/balance_table.tex
Added clines to tables

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,945.81 & 26,570.00 & 0.00 & 10,202.27 & 0.18 \\
 & Zestimate, Jan. 2018 & 320,176.82 & 27,148.19 & 0.00 & 9,364.98 & 0.26 \\
 & Change from Jan. 2018 to Jan. 2019 & 50,501.64 & 2,664.69 & 0.27 & -133.67 & 0.96 \\
\cline{1-7}
\multirow[c]{6}{3cm}{\textit{Panel B}} & Portion with bachelor's degree or higher (2010) & 0.25 & 0.01 & 0.07 & 0.01 & 0.39 \\
 & Number of jobs per sq. mile (2010) & 4,158.02 & 263.90 & 0.63 & 133.63 & 0.81 \\
 & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,178.12 & 0.25 \\
 & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 483.30 & 0.18 \\
 & Portion white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.07 \\
 & Share with commute under 15 min. (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
\cline{1-7}
\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.82 \\
\cline{1-7}
\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.67 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 10,202.27 & 0.18 \\
 & Zestimate, Jan. 2018 & 320,170.03 & 27,148.19 & 0.00 & 9,364.98 & 0.26 \\
 & Change from Jan. 2018 to Jan. 2019 & 50,491.60 & 2,664.69 & 0.27 & -133.67 & 0.96 \\
\cline{1-7}
\multirow[c]{6}{3cm}{\textit{Panel B}} & Portion with bachelor's degree or higher (2010) & 0.25 & 0.01 & 0.07 & 0.01 & 0.39 \\
 & Number of jobs per sq. mile (2010) & 4,158.02 & 263.90 & 0.63 & 133.63 & 0.81 \\
 & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,178.12 & 0.25 \\
 & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 483.30 & 0.18 \\
 & Portion white (2010) & 0.60 & 0.04 & 0.00 & 0.02 & 0.07 \\
 & Share with commute under 15 min. (2010) & 0.29 & -0.01 & 0.02 & -0.00 & 0.27 \\
\cline{1-7}
\textit{Panel C} & For cause & 0.12 & 0.01 & 0.68 & 0.00 & 0.82 \\
\cline{1-7}
\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.67 \\
\cline{1-7}
\bottomrule
\end{tabular}
